A Cloud Native Approach to Adversarial Robustness of Neural Networks

### 2024-03-29 plots/cifar/aft_comparison.tex
update plots

\begin{table}
\caption{Comparison of AFR Models on the CIFAR dataset.}
\label{tab:cifar}
\begin{tabular}{llrlrr}
\toprule
 & AIC & Concordance & BIC & Mean $S(t;\theta)$ & Median $S(t;\theta)$ \\
\midrule
weibull & -550 & 0.856 & -550 & 0.266 & 0.219 \\
cox & -- & 0.856 & -- & 0.202 & 0.254 \\
log_logistic & -562 & 0.857 & -562 & 0.258 & 0.215 \\
log_normal & -568 & 0.857 & -568 & 0.258 & 0.216 \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table*}
\caption{Comparison of AFR Models on the CIFAR dataset.}
\label{tab:cifar}
\begin{tabular}{llrlrr}
\toprule
 & AIC & Concordance & BIC & Mean $S(t;\theta)$ & Median $S(t; \theta)$ \\
\midrule
Weibull & 527.37 & 0.72 & 527.37 & 1.83 & 0.97 \\
Cox & -- & 0.73 & -- & 0.85 & 0.32 \\
Log Logistic & 544.73 & 0.74 & 544.73 & 1.66 & 1.05 \\
Log Normal & 532.28 & 0.74 & 532.28 & 1.61 & 1.05 \\
\bottomrule
\end{tabular}
\end{table*}

### 2024-03-29 plots/mnist/aft_comparison.tex
update plots

\begin{table*}
\caption{Comparison of AFR Models on the MNIST dataset.}
\label{tab:mnist}
\begin{tabular}{llrlrr}
\toprule
 & AIC & Concordance & BIC & Mean $S(t;\theta)$ & Median $S(t; \theta)$ \\
\midrule
Weibull & -1631.26 & 0.90 & -1631.26 & 0.15 & 0.09 \\
Cox & -- & 0.90 & -- & 0.11 & 0.05 \\
Log Logistic & -1842.71 & 0.90 & -1842.71 & 0.14 & 0.08 \\
Log Normal & -1799.93 & 0.90 & -1799.93 & 0.14 & 0.08 \\
\bottomrule
\end{tabular}
\end{table*}

>>>>

\begin{table*}
\caption{Comparison of AFR Models on the MNIST dataset.}
\label{tab:mnist}
\begin{tabular}{llrlrr}
\toprule
 & AIC & Concordance & BIC & Mean $S(t;\theta)$ & Median $S(t; \theta)$ \\
\midrule
Weibull & 133.22 & 0.80 & 133.22 & 2.10 & 0.81 \\
Cox & -- & 0.80 & -- & 0.63 & 0.28 \\
Log Logistic & 93.77 & 0.77 & 93.77 & 1.22 & 0.82 \\
Log Normal & 104.95 & 0.76 & 104.95 & 1.21 & 0.84 \\
\bottomrule
\end{tabular}
\end{table*}
